Circular Regression Trees and Forests with an Application to Probabilistic Wind Direction Forecasting

### 2020-04-16 pkg/circtree/inst/wind_paper/draft/draft.Rnw
Update computational details
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@3010 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: fd4ab622ddc4a10971a21c6bffe15b344f0c3bd7

For the circular GLM considered as reference model the corresponding
implementation is provided in the \textsf{R} package \textbf{circglmbayes} by
\cite{Mulder+Klugkist:2017}. In particular the function \code{circGLM} is
applied to estimates the intercept and regression coefficient along with the
concentration parameter.

>>>>

For the circular generalized linear model considered as reference model the corresponding
implementation is provided in the \textsf{R} package \textbf{circglmbayes} by
\cite{Mulder+Klugkist:2017}. In particular the function \code{circGLM} is
applied to estimates the intercept and regression coefficient along with the
concentration parameter.

The computation time on a standard computer is in the order of 10\,milliseconds
for the circular fit (used for the persistency and the climatological model),
seconds for the estimation of the linear model and the circular tree, and from
a few minutes to an hour for the estimation of the circular forest; the latter
strongly depends on the number of covariates employed and, hence, varies
between Innsbruck and Vienna Airport. However, for a single station and
forecast step, the persistency and linear models must be re-estimated for each
time of interest, and independent climatological models have to be fitted for
all times of interest within a single calendar year, whereas for all times of interest only one 
circular tree and circular forest model is required.

%The computation time on a standard computer is in the order of 10\,milliseconds
%for the circular fit (used for the persistency and the climatological model),
%seconds for the estimation of the linear model and the circular tree, and from
%a few minutes to an hour for the estimation of the circular forest; the latter
%strongly depends on the number of covariates employed and, hence, varies
%between Innsbruck and Vienna Airport. However, the persistency and linear
%models must be re-estimated for each time point in the validation data set, and
%independent climatological models have to be estimated for all the time points
%within one calendar year which exist in the validation period, whereas only one
%model is needed for the circular tree and the circular forest valid for all
%times points in the validation data set.
